A statistically consistent approach to chemical tagging

### 2018-11-16 article/ms.tex
foo

@@

>>>>

\author{MML people and GALAH people}

@@

\begin{figure*}
	\includegraphics[width=1.0\textwidth]{experiments/galah-experiment-4-log-L-hist.png}
	\caption{Log likelihoods $\mathcal{L}\left(\data|\vec\Psi\right)$ of optimised
			 models using \Galah\ data in Experiment 4 with four latent factors
			 and four components ($J = 4$, $K = 4$). The columns indicate different
			 methods to initialise the component parameters ($\pi$, $\scoremeans$,
			 $\scorecovs$), and the rows represent different methods to initialise
			 the latent factors ($\factorloads$). Each combination of initialisation
			 procedure has 30 models where E-M was run until a threshold of $10^{-8}$
			 was reached in $\log{L}$.}
	\label{fig:galah-experiment-4-log-L}
\end{figure*}
